---
title: "feowR"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package makes easier to work with Freshwater Ecoregions of the World (FEOW) data, as it downloads and loads the shapefile files to the working directory.

We can start loading the package and using its main function, `read_feow()`

```{r setup}
library(feowR)

feow_sf <- read_feow()
```

Then we can see that the packages has a list of all ecoregions provided

```{r}
ecoregions_list
```

Now that we have the shapefile and the list of all ecoregions, we can select one big region (called *realm*) to study.

Let's take a look at the Freshwater Ecoregions of Neotropical region!

We just have to join our datasets and filter the `realm == "Neotropical"`, then we can plot it!

```{r, dpi = 600, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)

feow_sf |>
  left_join(ecoregions_list, by = join_by("FEOW_ID" == "id")) |>
  filter(realm == "Neotropic") |>
  ggplot()+
  geom_sf()
```




